\textbf{Interaction.} The interaction energy between particles in configuration $\gamma = \{x_1, ..., x_N\}$, where $x_i$ is the space coordinate of the $i$-th particle and $N$ is the number of points (particles) in the configuration $\gamma$, is defined as follows
\begin{equation*}
	W_{N_v}(\gamma) = \frac{1}{2} \sum_{x,y \in \gamma} \Phi_{N_v} (x,y)
\end{equation*}
where $\Phi_{N_v}$ is given by the Curie-Weiss interaction
\begin{equation}
	\label{def:curie-weiss-pot}
	\Phi_{N_v}(x, y) = -\frac{J_1}{N_v} + J_2\sum_{l=1}^{N_v} I_{\Delta_l}(x) I_{\Delta_l}(y),
\end{equation}
and $I_{\Delta_l}(x)$ is the indicator of $\Delta_l$
\begin{equation}
	\label{def:I}
	I_{\Delta_l} (x) = \left\{
	\begin{array}{ll}
		1, \quad x \in \Delta_l,
		\\
		0, \quad x \notin \Delta_l.
	\end{array}
	\right.
\end{equation}
The first term in $\Phi_{N_v}$ describes the pairwise attraction between all particles and is characterized by $J_1 > 0$. The second term in $\Phi_{N_v}$ describes the repulsion between two particles contained within the same cell $\Delta_l$ and is characterized by $J_2 > 0.$ For convenience, in $W_{N_v}$ above the self-interaction term $\Phi_{N_v}(x,x)$ is included, which does not affect the physics of the model. Two cases are possible, either two particles belong to the same cell or to different ones. Explicitly, one has
\begin{equation}
	\Phi_{N_v}(x, y) = \left\{
	\begin{array}{ll}
		-\frac{J_1}{N_v} + J_2, & \text{when particles are in the same cell,}
		\\
		-\frac{J_1}{N_v}, & \text{otherwise.}
	\end{array}
	\right.
\end{equation}
In~\cite{KKD20}, the notation $\abs{\gamma}$ was used to denote the number of points (particles) in configuration $\gamma$, thus $\abs{\gamma} \equiv N$.

\begin{mdframed}[linecolor=black,linewidth=1pt,leftline=true]
	If the notation from~\cite{HansenMcDonald13} is followed, the previous formulas can be rewritten as follows. The space coordinate of the $i$-th particle is denoted by $\vb{r}_i$, and thus the configuration of $N$ particles is defined by $\gamma = \{\vb{r}^N\}$, where $\vb{r}^N \equiv \vb{r}_1, ..., \vb{r}_N$. The interaction energy is expressed as (cf.~\cite[eq.~(2.5.16)]{HansenMcDonald13})
	\begin{eqnarray*}
		W_{N_v}(\vb{r}^N) & = & \frac{1}{2} \sum_{\vb{r}_i,\vb{r}_j \in \gamma} \Phi_{N_v} (\vb{r}_i,\vb{r}_j)
		\\
		& = & \frac12 {\sum_{i=1}^N \sum_{j=1}^N} \Phi_{N_v} (\vb{r}_i,\vb{r}_j),
	\end{eqnarray*}
	with
	\begin{equation*}
		\Phi_{N_v}(\vb{r}_i, \vb{r}_j) = -\frac{J_1}{N_v} + J_2\sum_{l=1}^{N_v} I_{\Delta_l}(\vb{r}_i) I_{\Delta_l}(\vb{r}_j),
	\end{equation*}
	and
	\begin{equation*}
		I_{\Delta_l} (\vb{r}) = \left\{
		\begin{array}{ll}
			1, \quad \vb{r} \in \Delta_l,
			\\
			0, \quad \vb{r} \notin \Delta_l.
		\end{array}
		\right.
	\end{equation*}
	Unlike~\cite[eq.~(2.5.16)]{HansenMcDonald13}, we do not exclude term with $i = j$ in the expression for $W_{N_v}$ due to the self-interaction.
\end{mdframed}


	\textbf{Stability.} For stability of interaction the following condition must hold
\begin{equation*}
	J_2 > J_1
\end{equation*}
to satisfy the following inequality~\cite{KKD20,Ruelle70}
\begin{equation}
	\int_{V} \Phi_{N_v}(x,y) {\rm d}y > 0, \quad \text{for all } x \in V.
\end{equation}
Note that there is one contribution to this integral from a cell containing the coordinate $x$, and $(N_v - 1)$ contributions from the other cells:
\begin{eqnarray*}
	\int_{V} \Phi_{N_v}(x,y) {\rm d}y & = & \left(-\frac{J_1}{N_v} + J_2\right)v - (N_v - 1) \frac{J_1}{N_v}v
	\\
	& = & (J_2 - J_1)v > 0.
\end{eqnarray*}
The ratio of the two energy constants is denoted by
$$a = J_2/J_1,$$
and thus $a > 1.$

\textbf{The grand partition function} (GPF) is expressed as follows~\cite[eqs.~(2.4.6) and~(2.3.13)]{HansenMcDonald13}
\begin{equation*}
	\Xi = \sum_{N=0}^{\infty}\frac{z^N}{N!} \int_{V} \dotsc \int_{V} \exp(-\beta W_{N_v}(\gamma)) {\rm d} x_1 \dotsc {\rm d} x_N
\end{equation*}
where $z$ is the activity
\begin{equation*}
	z = \frac{\exp(\beta \mu)}{\Lambda^3},
\end{equation*}
$\beta = 1/(k_{\rm B} T)$ the inverse temperature, $k_{\rm B}$ the Boltzmann constant, $T$ the temperature, $\mu$ the chemical potential, $\Lambda = (2\pi\beta\hbar^2/m)^{1/2}$ the de Broglie thermal wavelength, $\hbar$ the Planck constant, $m$ the mass of a particle. In GPF the integration goes over all configurations with $N$ particles and then the summation goes over all positive integer values of $N$.

\begin{mdframed}[linecolor=black,linewidth=1pt,leftline=true]
	Alternatively, in notation from~\cite{HansenMcDonald13}, the GPF is expressed as [cf. eqs.~(2.4.6) and~(2.3.13)]
	\begin{equation}\label{ZGR}
		\Xi=\sum_{N=0}^{\infty}\frac{z^N}{N!}Z_N,
	\end{equation}
	where $Z_N$ is the configuration integral:
	\begin{equation}
		Z_N = \int\exp(-\beta W_{N_v}(\vb{r}^N)){\rm d}\vb{r}^N
	\end{equation}
	with ${\rm d} \vb{r}^N \equiv {\rm d}{\vb r_1} \dotsc {\rm d}{\vb r_N}$.
\end{mdframed}


	\subsection{Partition function transformation}
Note the following summation:
\begin{equation}
	\sum_{\vb{r}_i,\vb{r}_j \in \gamma} 1 = N^2 = \abs{\gamma}^2.
\end{equation}
The GPF is then explicitly written as
\begin{equation}
	\label{eq:gpf1}
	\Xi = \sum_{N=0}^{\infty} \frac{\Lambda^{-3N}}{N!}\int \exp[\beta\mu N + \frac{p}{2N_{v}} N^2 - \frac{ap}{2} \sum_{x,y \in \gamma} \sum_{l=1}^{N_v} \mathbb{I}_{\Delta_l}(x)\mathbb{I}_{\Delta_l}(y)] {\rm d} x_1 \dotsc {\rm d} x_N.
\end{equation}

\begin{mdframed}[linecolor=black,linewidth=1pt,leftline=true]
	Alternatively
	\begin{equation}
		\label{eq:gpf1_alt}
		\Xi = \sum_{N=0}^{\infty} \frac{\Lambda^{-3N}}{N!}
		\int
		\exp[\beta\mu N + \frac{\beta^*}{2N_{v}} N^2 - \frac{a\beta^*}{2} \sum_{\vb{r}_i,\vb{r}_j \in \gamma} \sum_{l=1}^{N_v} \mathbb{I}_{\Delta_l}(\vb{r}_i)\mathbb{I}_{\Delta_l}(\vb{r}_j)] {\rm d} \vb{r}^N.
	\end{equation}
\end{mdframed}
Equations~\eqref{eq:gpf1} and~\eqref{eq:gpf1_alt} can be compared with~\cite[(2.5)]{KKD20}.

For a given $l = 1, \cdots , N_v$ and a configuration $\gamma$, we set $\gamma_l = \gamma \cap \Delta_l,$ that is, $\gamma_l$ is the part of the configuration contained in $\Delta_l$. Then, $N_l \equiv \abs{\gamma_l}$ stands for the number of points (particles) of $\gamma$ contained in $\Delta_l$.

	\textbf{Some useful formulas}. Note the following summation results:
\begin{equation}
	\label{eq:1}
	N_l \equiv \abs{\gamma_l} = \sum_{x \in \gamma_l} 1 = \sum_{x \in \gamma} \mathbb{I}_{\Delta_l}(x) = \sum_{j=1}^{N} \mathbb{I}_{\Delta_{l}}(x_j),
\end{equation}
\textbf{\textcolor{Red}{Question:}} Can $x \in \gamma_l$ and $x \in \Delta_l$ be used interchangeably?
\begin{equation}
	\label{eq:2}
	\sum_{l=1}^{N_v} N_l = N, \quad \sum_{l=1}^{N_v} \abs{\gamma_l} = \abs{\gamma},
\end{equation}
\begin{equation}
	\label{eq:3}
	\left(\sum_{l=1}^{N_v} N_l \right)^2 = N^2, \quad \left(\sum_{l=1}^{N_v} \abs{\gamma_l} \right)^2 = \abs{\gamma}^2.
\end{equation}
\begin{equation}
	\label{eq:4}
	\sum_{x \in \gamma} \rightarrow \sum_{l=1}^{N_v} \sum_{x \in \Delta_l};
\end{equation}
\begin{equation}
	\label{eq:5}
	\sum_{x,y \in \gamma} \rightarrow \sum_{l,l'=1}^{N_v} \sum_{x \in \Delta_l} \sum_{y \in \Delta_{l'}}.
\end{equation}
\begin{equation}
	\label{eq:6}
	\sum_{x \in \Delta_l}\sum_{y \in \Delta_l'} 1 = N_l N_{l'} = \abs{\gamma_l} \abs{\gamma_{l'}}.
\end{equation}
\begin{equation}
	\label{eq:sumII}
	\sum_{x,y \in \gamma}\sum_{l=1}^{N_v} \mathbb{I}_{\Delta_l}(x) \mathbb{I}_{\Delta_{l}}(y) = \sum_{l=1}^{N_v} N_l^2 \equiv \sum_{l=1}^{N_v} \abs{\gamma_l}^2.
\end{equation}
Combining these formulas, we get
\begin{eqnarray}
	\sum_{x,y \in \gamma} \Phi_{N_v}(x,y) & = & \sum_{l,l'=1}^{N_v} \sum_{x \in \Delta_l} \sum_{y \in \Delta_{l'}} \Phi_{N_v}(x,y)
	\nonumber\\
	& = & - \frac{J_1}{N_v} \left(\sum_{l=1}^{N_v} N_l\right)^2 + J_2\sum_{l=1}^{N_v}N_l^2
	\\
	& = & - \frac{J_1}{N_v} \left(\sum_{l=1}^{N_v} \abs{\gamma_l}\right)^2 + J_2\sum_{l=1}^{N_v}\abs{\gamma_l}^2
\end{eqnarray}